# Results
```{r method-source-data-prep, child = "markdown/data_prep.rmd"}
```
```{r method-source-data-anal, child = "markdown/data_analysis.rmd", eval = FALSE}
```

All analysis were conducted using `r r_citations$r`. `r r_citations$pkgs`.

In the current version of the manuscript, we included `r nrow(study_overview)` data sets from `r nrow(publications_overview)` publications, spanning `r length(unique(full_data$subject))` participants contributing `r nrow(full_data)` trials. A complete list of the included publications can be found in the appendix **REFERENCE**.

The publications included in this database span from the year `r min(publications_overview$conducted)` to `r max(publications_overview$conducted)`. The complete data spans `r nrow(procedure_data)` measurement sessions, `r sum(procedure_data$repetition_location == "lab")` of which were conducted in the lab and `r sum(procedure_data$repetition_location == "online")` online.

```{r}
age_data <- study_overview %>% 
  mutate(participant_age = ifelse(participant_age == 99, NA, participant_age)) %>% 
  filter(!is.na(participant_age), !is.na(n_participants))
```

Sample composition ranged from `r min(study_overview$n_participants, na.rm = TRUE)` to `r max(study_overview$n_participants, na.rm = TRUE)` participants. On average, studies included `r mean(study_overview$n_participants, na.rm = TRUE)` participants ($\mu_{age} =$ `r weighted.mean(age_data$participant_age, age_data$n_participants, na.rm = TRUE)`,$\sigma_{age} =$ `r DescTools::SD(age_data$participant_age, weights = age_data$n_participants, na.rm = TRUE)`).

